### 2019-06-09 monograph/thesis/chapters/beautifiers.tex
Revert "Correções para linux"
This reverts commit 7b06cc8c2bcfdd290cc6dda351b7de9524f5d1cb.
Removed redundant \phantomsection text messages from all chapters
Moved What does coding is, section to beautifiers.tex from
monograph/thesis/chapters/theorybase.tex

% The \phantomsection command is needed to create a link to a place in the document that is not a
% figure, equation, table, section, subsection, chapter, etc.
%
% When do I need to invoke \phantomsection?
% https://tex.stackexchange.com/questions/44088/when-do-i-need-to-invoke-phantomsection
\phantomsection

% Is it possible to keep my translation together with original text?
% https://tex.stackexchange.com/questions/5076/is-it-possible-to-keep-my-translation-together-with-original-text
\chapter{Source Code Beautifiers}
\label{source_code_beautifiers}

@@

\medskip
% \begin{bluebox}
\begin{enumerate}[nosep,nolistsep]
    \item Add new lines after `\{' and before `\}
    \item Add new lines before `\{'
    \item Remove empty lines
    \item Add comment lines before function
    \item Add new lines after `;'
    \item Add new lines after `\}'
    \item Remove new lines
    \item Reduce whitespace
    \item Fix bad indentation
\end{enumerate}
% \end{bluebox}
\begin{flushright}\textcite{prettyPrinter}\end{flushright}

>>>>

\chapter{Source Code Beautifiers}
\label{source_code_beautifiers}

\section{\lang{What does coding is}{Programação de computadores}}

\lang{
    Coding is like writing and reading a book for the large people, you like it
    to look beautifully. Or at least do you expect such when you buy a book, for
    example, to learn programming for you first time \cite{howNovicesRead}.
    You expect:
    \begin{enumerate}
        \item
            Things to be well organized,
            so you do not get lost.
        \item
            The colors to be properly placed,
            so you do not get distracted from the main content.
        \item
            The spacing between paragraphs, words, chapters, sections
            subsections, etc, to be well adjusted.
            Not everything cluttered in only one file,
            line, function, class, or whatsoever so.
    \end{enumerate}
}{%
    Programar pode ser considerado pela maioria das pessoas como escrever um livro,
    e para tal,
    \advisor{busca~=se mais a ideia de facilidade de leitura.
    Existem livros muito horríveis de se ler:
    fontes inadequadas ou pequenas,
    com folhas que brilham contra a luz.
    }{gostar~=se mais caso este ``livro'' tenha uma boa aparência.
    }No mínimo espera~=se algumas características chave ao comprar~=se
    um livro \cite{visualizationsInAFunctionalProgramming}.
    Por exemplo,
    quando compra~=se um livro,
    \advisor{}{para aprender a programar pela primeira vez,
    }espera~=se que \cite{howNovicesRead}:
    \begin{enumerate}
        \item
            Seu conteúdo esteja bem organizado,
            para que o leitor não se perca durante sua leitura.
        \item
            Que suas cores \advisor{sejam}{estejam} propriamente escolhidas e
            utilizadas,
            para que elas não distraiam o leitor ou tirem o foco do principal,
            o conteúdo do livro.
        \item
            Que o espaçamento entre os parágrafos,
            palavras, capítulos, seções, subseções, etc, estejam propriamente ajustados,
            e não\advisor{}{ todo} aglomerado ou desordenado em um único parágrafo,
            frase, capítulo\advisor{.}{, etc.}
    \end{enumerate}
}

\advisor{}{%
    \subsection{\lang{Computer Assisted Programming}{Programação auxiliada}}

    \lang{%
        Your computer should help you with these unforeseen tasks.
        Why should I spend my precious time checking whether I am actually copying
        something space indented,
        when I am actually coping something tab indented?
        Perhaps we should sit and cry while waiting for some greater force to come
        and rescue us. Or may be you should stop crying and actually do something
        about other than keep waiting for you mommy to come and save you from the
        darkness growing behind you back leading you to endless unsleepy nights
        fixing your code just because everything just went wrong.
    }{%
        Seu computador deveria ajudar você com aquelas imprevistas tarefas.
        Por que eu deveria gastar meu precioso tempo verificando se algo que estou copiando,
        está indentado por ``TAB''\s ou espaços?
        Talvez devêssemos sentar e
        chorar enquanto aguardamos que alguma força maior do Universo venha e
        nos salve.
        Ou talvez você deva para de chorar e
        realmente fazer alguma coisa a respeito além de continuar esperando que sua mamãe venha e
        resgate você da escuridão crescendo pela suas costas levando você a infinitas noites
        acordado corrigindo seu código simplesmente por que tudo deu errado.
    }
}

@@

\medskip
% \begin{bluebox}
\begin{enumerate}[nosep,nolistsep]
    \item Add new lines after `\{' and before `\}
    \item Add new lines before `\{'
    \item Remove empty lines
    \item Add comment lines before function
    \item Add new lines after `;'
    \item Add new lines after `\}'
    \item Remove new lines
    \item Reduce whitespace
    \item Fix bad indentation
\end{enumerate}
% \end{bluebox}
\vspace{-4mm}\begin{flushright}\textcite{prettyPrinter}\end{flushright}
